### 2016-05-30 syntax.tex
cheers

\heading{Soundness of hash-based filters.} \tsnote{To do.}

@@

\heading{Soundness for mutable hash-based filters. } \tsnote{To do.}

>>>>

\heading{Soundness of hash-based filters.} \tsnote{To do.  Note that it makes sense to consider soundness both in the public and private hash setting.  NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions  It might be interesting to run some experiments, e.g. set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}

@@

\heading{Soundness for mutable hash-based filters. } \tsnote{To do.  Same comments as for the simple case, only it's more complicated here what it means to violate soundness.}
